---
title: "Task04_Compare_Relative_IC50"
author: "Andrew Stein"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
Prior toward running this code, you need to first install PharmacoGx (Task01) and  download the relevant datasets (Task02)
```{r}
  library(PharmacoGx)
  library(tidyverse)
```

##load in the data and find common naming in the files
```{r}
  load("PSets/CCLE.RData")
  load("PSets/GDSC.RData")
  common <- intersectPSet(list('CCLE'=CCLE,
                             'GDSC'=GDSC),
                              intersectOn=c("cell.lines", "drugs"), 
                              strictIntersect=TRUE)
```

## Plot distribution of IC50s
```{r}
  measure =  "ic50_published"
  ic50s = data.frame(
    CCLE_IC50 = as.vector(summarizeSensitivityProfiles(common$CCLE,sensitivity.measure = measure)),
    GDSC_IC50 = as.vector(summarizeSensitivityProfiles(common$GDSC,sensitivity.measure = measure)))
  
  ggplot(ic50s,aes(x=CCLE_IC50,y=GDSC_IC50)) +
    geom_point(alpha=0.5) + 
    geom_smooth() + 
    scale_x_log10() + 
    scale_y_log10() + 
    theme_bw() + 
    annotate("segment",x=1e-3,xend=1e3,y=1e-3,yend=1e3,linetype="dotted")
  
  
  
```


## Load in one dataset and start to explore correlations for
Commenting out the plot because now using the function further below
```{r}
  pSet = CCLE

  info     = sensitivityInfo(pSet)
  profiles = sensitivityProfiles(pSet)
  measures = sensitivityMeasures(pSet)
  
  log_ic50 = summarizeSensitivityProfiles(pSet,sensitivity.measure = "ic50_published") %>%
    log()

  x = log_ic50 %>%
    t() %>%
    cor(use="pairwise")

  #corrplot::corrplot(x)
  
  #keep only rows and columns
  
```

## Create a function for doing the correlation
```{r}

#look at cross correlations
pSet_corr = function(pSet) {
  
  #get the log_ic50 dataset
  log_ic50 = summarizeSensitivityProfiles(pSet,sensitivity.measure = "ic50_published") %>%
    log()

  x = log_ic50 %>%
    t() %>%
    cor(use="pairwise")

  corrplot::corrplot(x)
  return(x)
}
```

## Perform the cross correlation
```{r}
  cor.CCLE = pSet_corr(common$CCLE)
  cor.GDSC = pSet_corr(common$GDSC)
```

## Correlate the cross-correlations
Red highlight the case where both cross-correlations were less than zero

```{r}
  n       = nrow(cor.CCLE)
  drugs   = row.names(cor.CCLE)
  cor.cor = data.frame(CCLE = as.vector(cor.CCLE),
                       GDSC = as.vector(cor.GDSC),
                       drug1= rep(drugs,times=n),
                       drug2= rep(drugs,each=n),
                       num1 = rep(1:n,times=n),
                       num2 = rep(1:n,each=n)) %>%
            mutate(drugs= paste0(drug1,":",drug2),
                   Sign = ifelse(CCLE<0 & GDSC<0,
                                 "Both < 0",
                                 "At least one > 0")) %>%
    filter(num1<num2) #remove the self-correlations

  neg.cor = cor.cor %>%
    filter(CCLE<0 & GDSC<0)
  
  ggplot(cor.cor,aes(x=CCLE,y=GDSC,color=Sign)) +
    geom_point() + 
    geom_smooth(aes(color=NULL),show.legend = FALSE,method='loess') +
    ggrepel::geom_text_repel(data=neg.cor,aes(label=drugs),show.legend = FALSE) + 
    scale_color_manual(values=c("black","red")) + 
    theme_bw()
           
```
## Properties of R session
sessionInfo()
